TGI-spinal-power

### 2022-05-03 analysis/tgispine_lme_power.Rmd
running lmm power calculation

# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
model.cold <- lmer(VAScold ~ manipulation + (1+manipulation|ID), data = df_phs)
summary(model.cold)
```
# View the coefficients for each person (should vary, due to random slope model)
```{r}
coef(model.cold)
```

@@

Finally a third model where all predictors are added - manipulation, condition and cold location
Still just on cold ratings
```{r}
model.cold3 <- lmer(VAScold ~ manipulation + condition + cold_location +
                      (1+manipulation|ID), 
                    data = df_phs)
summary(model.cold3)
```

>>>>

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_phs$cold <- df_phs$VAScold/100
df_phs$warm <- df_phs$VASwarm/100
df_phs$burn <- df_phs$VASburning/100
df_phs$ID <- factor(df_phs$ID)

# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
model.cold <- lmer(cold ~ manipulation + (1|ID), data = df_phs)
summary(model.cold)
```
# View the coefficients for each person (should vary, due to random slope model)
```{r}
coef(model.cold)
```

# Running power analysis on simple model
```{r, include = FALSE}
# add more participants to the model, for simulation
model.coldN <- extend(model.cold, along ='manipulationTGI', n=10)
summary(model.coldN)
# extract fixed effects from the model
tgi_effect <- fixef(model.coldN)["manipulationTGI"]
# need to estimate minimum desired effect from the change in slope - considering values can range from 0-100, it might be simpler to think of these effect sizes as a proportion of 100 instead
# tgi_effect = -17.05 would perhaps leave an expected effect size of .17
# change the effect size to effect size of interest
fixef(model.coldN)["manipulationTGI"] <- 10

# then run power analysis
powerSim(model.coldN)
```

@@

Finally a third model where all predictors are added - manipulation, condition and cold location
Still just on cold ratings
```{r}
model.cold3 <- lmer(cold ~ manipulation + condition + cold_location +
                      (1|ID), 
                    data = df_phs)
summary(model.cold3)
```
